---
title: "ex17"
author: "Dan Wakeling"
date: "27/08/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)

```

## Number letter counts

If the numbers 1 to 5 are written out in words: one, two, three, four, five, then there are 3 + 3 + 5 + 4 + 4 = 19 letters used in total.

If all the numbers from 1 to 1000 (one thousand) inclusive were written out in words, how many letters would be used?


NOTE: Do not count spaces or hyphens. For example, 342 (three hundred and forty-two) contains 23 letters and 115 (one hundred and fifteen) contains 20 letters. The use of "and" when writing out numbers is in compliance with British usage.

```{r code one}

# end letters
in_end <- data.frame(
  number = c(1:9),
  letters = c(3, 3, 5, 4, 4, 3, 5, 5, 4)
)

# teens
in_teens <- data.frame(
  number = c(11:19),
  letters = c(6, 6, 8, 8, 7, 7, 9, 8, 8)
)

# tens
in_tens <- data.frame(
  number = seq(10, 90, by = 10),
  letters = c(3, 6, 6, 5, 5, 5, 7, 6, 6)
)

# hundreds
in_hundreds <- data.frame(
  number = seq(100, 900, by = 100),
  letters = in_end$letters + 7
)


```

# Compile Data Frame

```{r data frame}

df <- data.frame(
  number = 1:999)

# add logic for which to join
df_end <- df %>% 
  mutate(end = number %% 10,
         end_two = number %% 100) %>% 
  left_join(in_end,
            by = c("end" = "number")) %>% 
  mutate(letters = case_when(
    between(end_two, 11, 19) ~ NA_real_,
    TRUE ~ letters)) %>% 
  select(-end, -end_two)

# tens
df_tens <- df %>% 
  mutate(tens = number %% 100) %>% 
  left_join(in_tens,
            by = c("tens" = "number")) %>% 
  fill(letters) %>% 
  mutate(letters = case_when(
    tens %in% c(0:9, 11:19) ~ NA_real_,
    TRUE ~ letters)) %>% 
  select(-tens)

# teens
df_teens <- df %>% 
  mutate(teens = number %% 100) %>% 
  left_join(in_teens,
            by = c("teens" = "number")) %>% 
  select(-teens)

# hundreds
df_hundreds <- df %>% 
  left_join(in_hundreds,
            by = "number") %>% 
  fill(letters)

```

```{r join and add thousand}

# join
df_all <- bind_rows(
  df_end, df_tens, df_teens, df_hundreds) %>% 
  group_by(number) %>% 
  summarise(letters = sum(letters, na.rm = TRUE)) %>% 
  ungroup() %>% 
  # add and
  mutate(letters = case_when(
    number > 100 & number %% 100 > 0 ~ letters + 3,
    TRUE ~ letters)) %>% 
  # add thousand
  bind_rows(
    data.frame(
      number = 1000,
      letters = 11))


sum(df_all$letters)

```

