---
title: "ex19"
author: "Dan Wakeling"
date: "29/12/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)

```

## Counting Sundays

You are given the following information, but you may prefer to do some research for yourself.

1 Jan 1900 was a Monday.
Thirty days has September,
April, June and November.
All the rest have thirty-one,
Saving February alone,
Which has twenty-eight, rain or shine.
And on leap years, twenty-nine.
A leap year occurs on any year evenly divisible by 4, but not on a century unless it is divisible by 400.

How many Sundays fell on the first of the month during the twentieth century (1 Jan 1901 to 31 Dec 2000)?

```{r code one}

days_of_week <- c(rep(0, 6), 1)

years <- 1900:2000

days_year <- 1:365

months <- c(rep(1, 31),
            rep(2, 28),
            rep(3, 31),
            rep(4, 30),
            rep(5, 31),
            rep(6, 30),
            rep(7, 31),
            rep(8, 31),
            rep(9, 30),
            rep(10, 31),
            rep(11, 30),
            rep(12, 31))

cal <- expand_grid(years, months)

# add leap years
df_add <- data.frame(
  years = seq(1904, 2000, by = 4),
  months = 2)

cal2 <- bind_rows(cal, df_add) %>% 
  arrange(years, months) %>% 
  mutate(id = row_number(),
         first_of_month = case_when(
           lag(months, 1) == months ~ FALSE,
           TRUE ~ TRUE)) %>% 
  filter(id %% 7 == 0,
         first_of_month == TRUE,
         years > 1900)

nrow(cal2)

```

